---
title: "knapsack"
author: "Group 19"
date: "10/10/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

## Package lab6
This is the package contain three different functions for solving what is called the knapsack problem.

## Install package
```{r }
devtools::install_github("lmxblur/Adv_lab6", subdir="lab6")
```


## Dataframe to use for the questions
```{r}
suppressWarnings(RNGversion("3.5.9"))
set.seed(42)
n <- 1000000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000)
)
```


### Brute force search Question: How much time does it takes to run the algorithm for n = 16 objects?

```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500))
```

It takes 0.46 seconds.



### Dynamic programming Question: How much time does it takes to run the algorithm for n = 500 objects?

```{r}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))
```

It takes 0.64 seconds.



### Greedy heuristic Question: How much time does it takes to run the algorithm for n = 1000000 objects?

```{r}
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500))
```

It takes 0.25 seconds.



### Profile your code and optimize your code Question: What performance gain could you get by trying to improving your code?






### Parallelize brute force search Question: What performance gain could you get by parallelizing brute force search?

```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500, parallel=TRUE))
```



For small dataframes we do not gain better performance but if we take a bigger dataset the parallel brute force search is way better

For x = knapsack_objects[1:16,]

If parallel=FALSE it takes 0.46 seconds.

If parallel=TRUE it takes 2.07 seconds.


```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:22,], W = 3500))
system.time(brute_force_knapsack(x = knapsack_objects[1:22,], W = 3500, parallel=TRUE))
```

BUT for x = knapsack_objects[1:22,]

If parallel=FALSE it takes 33.02 seconds.

If parallel=TRUE it takes 30.56 seconds.
















